---
title       : Developing Data Products Work
subtitle    : Summary for My Shiny Application
author      : bincai
job         : Hadooper@Tencent
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      #
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview
- Goal
  - Write a shiny application with associated supporting documentation.
- Application
  - Normal (or Gaussian) distribution is a very commonly occurring continuous probability distribution
  - This Shiny application draw normal distribution curve according to user's input

---&twocol
## UI
*** =left
- Input parameters
  - mu: the mean or expectation of the distribution.
  - sigma: its standard deviation.
  - range: interval of axis x
- Output
  - Normal distribution parameters
  - Plot of distribution
- Widget
  - h5 for input
  - sliderInput for mu and sigma
  - radioButtons for range
  - textOutput for echoing input value
  - plotOutput for the plot

*** =right
```{r, eval = FALSE}
library(shiny)
shinyUI(pageWithSidebar(
 headerPanel("Bin's Work for ...!"),
 sidebarPanel(
  h5("This application ...." ),
  sliderInput(inputId = "mu", ...),
  sliderInput(...),
  radioButtons(inputId = "range",
    label = "Parameter range:",
    choices = list("-5, 5" = "FIVE",
                   "-10, 10" = "TEN",
                   ...))
 ),

 mainPanel(
  textOutput('text1'),
  plotOutput("nPlot")
 )
))
```

---&twocol
## Server
*** =left
- Operations
  - Using if-else to process radioButtons input to x.
  - renderText to combine input params.
  - renderPlot to plot normal distribution.


*** =right
```{r, eval = FALSE}
library(shiny)
shinyServer(
 function(input, output) {
  x <- reactive({      
   r=5
   if(input$range == "TEN")    r=10
   ....
   r
  }) 
  output$text1 <- renderText(
   paste( "....", {input$mu} ... )
  )
  output$nPlot <- renderPlot({ 
   r <- x()
   x <- seq(-r,r,length=1000)
   y <- dnorm(x,mean={input$mu}, 
              sd={input$sigma})
   plot(x, y, type="l", lwd=1)
  })
 }
)
```

---
## Summary
- Requirement Fulfillment
  - Widget: slider, radio buttons, textOutput, plotOutput
  - sever.R operations: get range from radio buttons, create output text
  - Reactive output: echo input parameter, draw the distribution
  - Document: meaning of parameters
- URL
  - Deployed application: https://caibinbupt.shinyapps.io/ddp2
  - server.R and ui.R code: https://github.com/caibinbupt/ddp2