---
title       : Developing Data Products Work
subtitle    : Summary for Regression Models Work
author      : bincai
job         : Hadooper@Tencent
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]     # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Summary
- Questions
  - Is an automatic or manual transmission better for miles per gallon (MPG)?
  - How different is the MPG between automatic and manual transmissions?
- Conclusion
  - Cars with a manual transmission have a slightly better than automatic for MPG.
  - This different is statistical INSIGNIFICANT.

---&twocol
## Exploratory Data
*** =left
- Data
  - mtcars is a data frame with 32 observations on 11 variables.
  - For regression, variables vs and am should be category.
```{r}
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
```
- Relationship between mpg and am
	- mpg (Miles/(US) gallon) vs. am (Transmission).
  - Boxplot it.
  - There's a good separation of groups based on gas mileage.

*** =right


```{r, fig.height=6, fig.width=6, echo = FALSE}
boxplot(mpg ~ am, 
        data = mtcars, 
        xlab = "Transmission (0 = automatic, 1 = manual)")
```

---&twocol
## Building the Model
*** =left
- Analysis of variance
	- There are 10 predictor variables in the data set.
	- Some may play bigger role to determination of mpg.
	- Using aov to fit an analysis of variance model.
```{r, echo = FALSE}
analysis <- aov(mpg ~ ., data = mtcars)
summary(analysis)
```

*** =right
- Fit the model
	- Variables with p-value below 0.05 are more important.
	- Variables cyl, disp, wt, drat and am are selected.
	- After fit the first two models, drat ans disp are droped. 
```{r}
lm <- lm(mpg ~ cyl + wt + am, data = mtcars)
summary(lm)
```

---&twocol
## Diagnostic the model
*** =left
- Result
	- The adjusted r-squared is 0.83
	- Compare with cylinders and weight, the ceofficient of the am variable is small (0.176).
	- p-value of am is 0.8933
	- We cannot reject the hypothesis that the coefficient of am is 0.
	- No discernible pattern found in diagnostic graph.
	
*** =right
- Diagnostic
```{r fig.height=6, fig.width=6, echo = FALSE }
par(mfrow = c(2, 2))
plot(lm)
```
